### 2013-03-26 doc/sosp13/tasks.tex
picture of context switch

@@

>>>>

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/context_switch_time.pdf}
    \end{center}
    \caption{Average context switch time with 1 and 6 active cores,
        with and without prefetching.}
    \label{fig:context-switch-time}
\end{figure}

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/context_switch_bw.pdf}
    \end{center}
    \caption{Context switch rate with prefetching. Once the total
        size of contexts sufficiently exceeds last-level cache, most
    prefetches go to main memory and the rate becomes limited to the
    off-chip bandwidth.}
    \label{fig:context-switch-time}
\end{figure}

@@

\TODO{Summary of what to write please expand: Reference above plots. Bandwidth of single socket is
    270Mcacheline/s. Each context is 4 cachelines: 1 for worker struct
    and 3 stack cachelines. We must read and write every context, so 8
    cacheline transfers per context switch. This asymptotically
    approaches 33.75Mcontexts/s as you increase the number of contexts
    (fewer and fewer in L3). Note that only 4+ cores reaches full rate
    because these westmere chips are balanced to not achieve full off-chip bandwidth until 4
    cores--bdmyers}
